\speculake: Hiding Malware in Speculative Execution

### 2018-12-10 paper/figures.tex
Minor fixes, added bandwidth recomputation to abstract and fixed cropping in figure 6

\newcommand{\FigNestedSpec}{
\begin{figure}[t]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.95\linewidth]{figures/ExSpectre_CR_Nested.png}
    \caption{\textbf{Nested Speculation}\,---\,%
    Using nested speculation for obfuscated key derivation. The payload uses 
    a sequence of indirect jumps controlled by the trigger to incrementally 
    construct a key exclusively in the speculative environment. Without the 
    trigger an analyst will need to evaluate every ordering of \textbf{all} indirect 
    jumps to reconstruct the key. While the \textit{decryption gadget} may be trivial 
    for an analyst to find, this allows for an encrypted blob in the payload 
    to remain inaccessible in the absence of the trigger. }
    \label{fig:nested-spec}

@@

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering  
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
        \caption{\textbf{Speculative Bandwidth}\,---\,%
        Using our speculative primitive, 1KB of data
        can be decrypted and exfiltrated at a speed between 5 and 6~Kbps from
        the speculative world with 20 redundant iterations per round (to ensure
        correctness). Increased channel width exfiltrates more data per round,
        but takes longer to measure the cache side channel. Optimal throughput is
        achieved with an 8-bit channel.}
    \label{fig:spec_bandwidth}
\end{figure}
}

>>>>

\newcommand{\FigNestedSpec}{
\begin{figure}[t]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.95\linewidth]{figures/ExSpectre_CR_Nested.pdf}
    \caption{\textbf{Nested Speculation}\,---\,%
    Using nested speculation for obfuscated key derivation. The payload uses 
    a sequence of indirect jumps controlled by the trigger to incrementally 
    construct a key exclusively in the speculative environment. Without the 
    trigger an analyst will need to evaluate every ordering of \textbf{all} indirect 
    jumps to reconstruct the key. While the \textit{decryption gadget} may be trivial 
    for an analyst to find, this allows for an encrypted blob in the payload 
    to remain inaccessible in the absence of the trigger. }
    \label{fig:nested-spec}

@@

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering  
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
        \caption{\textbf{Speculative Bandwidth}\,---\,%
        Using our speculative primitive, 1KB of data
        can be decrypted and exfiltrated at a speed of 5.38~Kbps from
        the speculative world with 20 redundant iterations per round (to ensure
        correctness). Increased channel width exfiltrates more data per round,
        but takes longer to measure the cache side channel. Optimal throughput is
        achieved with an 8-bit channel.}
    \label{fig:spec_bandwidth}
\end{figure}
}
